Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex
Take 80 on the intro

In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize a target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}

Without a target loss, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
We seek \emph{consistent} surrogates, which typically means the average deviation from the hypothesis and true ``regression function'' converges to 0 in probability.
Consistency is important as it is a precursor to excess risk bounds and rates, and we are particularly interested in consistent \emph{and convex} surrogates
% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
%We would also like our surrogate losses to be 
that are efficient in the prediction dimension, as this is one potential source of significant computational speedup.
%\jessiet{Adding the following two sentences: is this what you meant?}
%While prediction dimension is a well-studied problem (\S~\ref{subsec:complexity}), previous results bounding prediction dimension only apply within very specific settings.
Previous bounds on the prediction dimension of a consistent surrogate have been considered in isolation in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.

@@

\subsection{Consistency and calibration for discrete convex losses}\label{subsec:convex-surrogates}

>>>>

In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize a target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
Without a target loss, one typically starts with a statistic of the data they would like to estimate instead, such as the conditional expected value or an $\alpha$-quantile.
We seek \emph{consistent} surrogates, which typically means the average deviation from the hypothesis and true ``regression function'' converges to 0 in probability.
Consistency is important as it is a precursor to excess risk bounds and rates, and we are particularly interested in consistent \emph{and convex} surrogates.
% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
%We would also like our surrogate losses to be

Surrogate losses take predictions $u \in \reals^d$ and measure their error against observed outcomes.
There is a natural tension between consistency and the prediction dimension $d$, as increasing the prediction dimension yields more degrees of freedom to link a surrogate prediction to the ``correct'' one in the original space, but also increases the computational expense of the problem.
We therefore desire a consistent surrogate with a low prediction dimension, as this is one potential source of significant computational speedup.
Prediction dimension bounds have been well-studied in the literature, typically through proxies like calibration (\S~\ref{subsec:calibration}) and property elicitation (\S~\ref{subsec:properties}).
Consider structured prediction settings, where the number of possible outcomes can grow exponentially fast; a surrogate with logarithmic dimension can enable the optimization of otherwise expensive problems.
%\jessiet{Adding the following two sentences: is this what you meant?}
%While prediction dimension is a well-studied problem (\S~\ref{subsec:complexity}), previous results bounding prediction dimension only apply within very specific settings.
Previous bounds on the prediction dimension of a consistent surrogate have been considered in isolation in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.

@@

\subsection{Calibration}\label{subsec:calibration}
